On the presentation of orthogonal groups over polynomial rings

### 2019-05-05 dl-paper.tex
Moved K-a-b to a separate subsection

In fact, we could prove something a little bit stronger.
\begin{lemma} \label{K-a-b}
 Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
 the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and
  $g_0 \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$.

 The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
 \begin{itemize}
  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
 \end{itemize}
\end{lemma}
\begin{proof}

 Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
 Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.

@@

\begin{corollary} Suppose $g$ is an element of $P_\alpha(0) \cap K(A[X], M[X])$. Then $ev^*_{X=0}(S_\alpha(a, g))$ lies in the subgroup $U(Z_+(\alpha), M)$. \end{corollary}
\begin{proof}
 By~\cref{Kgen-strong} and~\cref{P0_normal} $g$ can be expressed as a product of elements 
 $z_\beta(Xf, \xi)$, $\beta\in\Phi\setminus\{\pm \alpha\}$, $c_\gamma(f, X\xi)$ for some $\gamma$ orthogonal to $\alpha$, $x_{-\alpha}(X^2f)$, $x_{\alpha}(f)$.

 It remains to notice that the only factors in the right-hand sides of in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} which do not vanish after evaluation at $X=0$
  are those of the form $x_\beta(m)$ for some $\beta \in Z_+(\alpha)$.
\end{proof}

@@

>>>>

@@

\begin{comment}
\begin{corollary} Suppose $g$ is an element of $P_\alpha(0) \cap K(A[X], M[X])$. Then $ev^*_{X=0}(S_\alpha(a, g))$ lies in the subgroup $U(Z_+(\alpha), M)$. \end{corollary}
\begin{proof}
 By~\cref{Kgen-strong} and~\cref{P0_normal} $g$ can be expressed as a product of elements 
 $z_\beta(Xf, \xi)$, $\beta\in\Phi\setminus\{\pm \alpha\}$, $c_\gamma(f, X\xi)$ for some $\gamma$ orthogonal to $\alpha$, $x_{-\alpha}(X^2f)$, $x_{\alpha}(f)$.

 It remains to notice that the only factors in the right-hand sides of in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} which do not vanish after evaluation at $X=0$
  are those of the form $x_\beta(m)$ for some $\beta \in Z_+(\alpha)$.
\end{proof}
\end{comment}

@@

\subsection{The subgroups $K(\alpha, \beta)$ and their properties}
\begin{df}
 Let $\alpha, \beta$ be a pair of nonopposite roots of $\Phi$. Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
 generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
 \end{enumerate}
\end{df}
It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$.
In fact, as the proposition below shows the opposite inclusion is also true.

\begin{prop} \label{K-a-b}
 Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
 the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$.
\end{prop}
\begin{proof}
 Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
 Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
